Excel fun

### 2022-07-13 Excel fun.Rmd
More Excel experiments.

>>>>

## Final version?
```{r}
excel <- read_excel("Data/OPXfinans2.xlsx")
excel <- clean_names(excel)

```

## Final final?
```{r}
excel <- read_excel("Data/OPXfinans_final.xlsx")
excel <- clean_names(excel)

excel
united <- excel |> 
  unite(entry, c(category, name), sep = "_")
united <- clean_names(united)
united <- united |> 
  select(-sub_category)
united_wide <- united |> 
  pivot_wider(names_from = entry, values_from = value) |> 
  clean_names()
united_wide

united_wide |> 
  mutate(
    KPI = expenses_fundraising / revenue_private_contributions * 100
  ) |> 
  select(year, firm, KPI) |> 
  ggplot(aes(as.factor(year), KPI)) +
  geom_col()

test <- excel
test$result <- excel |> 
  group_by(category) |> 
  summarise(
    value = sum(value)
  ) |> 
  pivot_wider(names_from = category, values_from = value) |> 
  summarise(
    result = Revenue - Expenses
  ) |>
  toString() |> 
  as.numeric()
test

excel |> 
  mutate(
    value = ifelse(category == "Expenses" | category == "Liability", -value, value)
  )
excel |> 
  filter(year == 2020) |> 
  mutate(
    total = sum(value)
  )

excel
```
